---
title: "Code for NFL Draft 2021 Insight"
author: "Marissa Troiano-Yang"
date: "4/1/2021"
output: html_document
---
Here is the code I used for "Insights for NFL Draft 2021."

#Load Packages

```{r}
library(RMySQL)
library(DBI)
pacman::p_load(magrittr, tidyverse)
library(gridironaiR)
library(GGally)
library(dplyr)
```

#Connect and Query SQL database

```{r}
connection <- dbConnect(MySQL(), user='gridironai', password='thenameofthewind', dbname='gridironai', host='footballai-db-prod.cxgq1kandeps.us-east-2.rds.amazonaws.com')

team_data_pff <- dbGetQuery(connection,
"SELECT * 
FROM 
        gridironai.dim_team_data_pff
ORDER BY 
        season DESC,
        pfr_franchise_code_id ASC")

team_data_pfr_rolling_avg <- dbGetQuery(connection,
"SELECT * 
FROM 
        gridironai.dim_team_data_pfr_rolling_avg
ORDER BY 
        season DESC,
        player_team_pfr_franchise_code_id ASC")

dbDisconnect(connection)
```

#Data Cleaning

To clean and subset the data for analysis, I removed the 3 game averages, Pro Football Reference grades, and any data related to the opponent. To see the total wins per team each season, I compared the final team and opponent scores and saved the data in a new column. I edited the team_name column for readability, grouped data by the team and season, then determined the sum of each variable for the season.

```{r}
team_data_pfr <- team_data_pfr_rolling_avg[,1:135] %>% 
        subset(week <= 17)

team_data_pfr %>% 
        season_week_to_char()

drop_cols <- c("week", "attendance", "home_away_ind", "team_q1", "team_q2", "team_q3", "team_q4", "opponent_q1", "opponent_q2", "opponent_q3", "opponent_q4", "defense_pass", "defense_rush", "defense_tot", "defense_tovr", "offense_pass", "offense_rush", "offense_tot", "offense_tovr", "specialteams_fgxp", "specialteams_ko", "specialteams_kr", "specialteams_p", "specialteams_pr", "specialteams_tot", "total", "q1_margin", "q2_margin", "q3_margin", "q4_margin", "margin_of_victory", "time_of_posession_diff")

opp_cols <- team_data_pfr %>% 
        select(ends_with("_opp")) %>% 
        colnames() 

team_data_agg <- team_data_pfr %>% 
        mutate(wins = if_else(team_data_pfr$team_final > team_data_pfr$opponent_final, 1, 0)) %>%
        rename(team_name = player_team_pfr_franchise_code_id) %>% 
        relocate(wins, .after = season) %>% 
        select(-one_of(c(drop_cols, opp_cols))) %>% 
        group_by(team_name, season) %>% 
        summarise_if(is.numeric, sum, na.rm = TRUE) %>% 
        mutate(yards_per_play = (passing_yds + rushing_yds) / (passing_att + rushing_att)) %>% 
        arrange(team_name, desc(season))

```
#Exploratory Data Analysis

Next I split the data by team and took the sum of all variables from 1970-2020 (regular season games) and then graphed this information for a visual representation.


```{r}
team_averages <- team_data_agg %>% 
        group_by(team_name) %>% 
        summarise_at(vars(-season), sum) %>% 
        arrange(desc(wins)) %>% 
        print(n = 32)
team_averages

seasonsPerTeam <- team_data_agg %>% 
        arrange(wins) %>% 
        ggplot(aes(x = season, y = reorder(team_name, -season), color = season)) +
        labs(title = "Number of Seasons Per Team", x = "Seasons", y = "Team Name") +
        guides(color = "none") +
        geom_point()

seasonsPerTeam
```
I then looked at teams vs wins from 2002-2020. Teams with a high number of wins in 2020 include KAN, GNB, BU and teams with a low number of wins include JAX, NYJ, ATL.
```{r}
phi_wins <- subset(team_data_agg, team_name == "PHI") %>% 
        ggplot(aes(x = season, y = wins, color = wins)) +
        labs(title = "PHI Number of Wins Per Season", x = "Season", y = "Wins") +
        scale_y_continuous(breaks=c(1:17)) +
        geom_line() +
        geom_point()
phi_wins

jax_wins <- subset(team_data_agg, team_name == "JAX") %>% 
        ggplot(aes(x = season, y = wins, color = wins)) +
        labs(title = "JAX Number of Wins Per Season", x = "Season", y = "Wins") +
        scale_y_continuous(breaks=c(1:17)) +
        geom_line() +
        geom_point()
jax_wins

nyj_wins <- subset(team_data_agg, team_name == "NYJ") %>% 
        ggplot(aes(x = season, y = wins, color = wins)) +
        labs(title = "NYJ Number of Wins Per Season", x = "Season", y = "Wins") +
        scale_y_continuous(breaks=c(1:17)) +
        geom_line()+
        geom_point()
nyj_wins

team_wins <- team_data_agg %>% 
        ggplot(aes(x = season, y = wins, color = wins)) +
        labs(title = "Number of Wins Per Season", x = "Season", y = "Wins") +
        geom_line() +
        facet_wrap(~ team_name)
team_wins

wins_2020 <- subset(team_data_agg, season == 2020) %>%
        ggplot(aes(x = wins, y = reorder(team_name, wins), color = wins)) +
        labs(title = "Number of Wins in 2020", x = "Wins", y = "Team Name") +
        geom_point(color = "steelblue")
wins_2020
```
#Linear Regression Model

Now for some predictions! I decided to use a Linear Regression Model to see which predictors have a strong relationship with the number of wins for the 2020 NFL season.
```{r}
lr_model_1 <- lm(wins ~ time_of_possession + first_downs + fourth_down_conv_att + fourth_down_conv_cmp +
                         penalties + penalties_yds + third_down_conv_att + third_down_conv_cmp + total_yards + turnovers +
                         all_td + safety_md + fumbles + fumbles_forced + fumbles_rec + fumbles_rec_td + fumbles_rec_yds + 
                         kicking_fga + kicking_fgm + kicking_xpa + kicking_xpm + passing_two_pt_md + passing_att + passing_cmp + 
                         passing_rating + passing_sacked + passing_sacked_yds + passing_td + passing_yds + punting_tot + punting_blocked +
                         punting_yds + puntret_tot + puntret_td + puntret_yds + receiving_rec + receiving_targets + receiving_td +
                         receiving_yds + rushing_att + rushing_td + rushing_yds + kickret_tot + kickret_td + kickret_yds + defense_qb_hits +
                         defense_sacks + defense_tackles_assists + defense_tackles_combined + defense_tackles_loss + defense_tackles_solo +
                         defense_int + defense_int_td + defense_int_yds + defense_pass_defended + yards_per_play, data = team_data_agg)

summary(lr_model_1)

resid <- lr_model_1$residuals
hist(resid)

par(mfrow = c(2,2))
plot(lr_model_1)

predictors_df <- team_data_agg %>% 
        select(time_of_possession, first_downs, fourth_down_conv_att , fourth_down_conv_cmp , penalties , penalties_yds , third_down_conv_att , third_down_conv_cmp , total_yards , turnovers , all_td , safety_md , fumbles , fumbles_forced , fumbles_rec , fumbles_rec_td , fumbles_rec_yds , kicking_fga , kicking_fgm , kicking_xpa , kicking_xpm , passing_two_pt_md , passing_att , passing_cmp , passing_rating , passing_sacked , passing_sacked_yds , passing_td , passing_yds , punting_tot , punting_blocked ,punting_yds , puntret_tot , puntret_td , puntret_yds , receiving_rec , receiving_targets , receiving_td , receiving_yds , rushing_att , rushing_td , rushing_yds , kickret_tot , kickret_td , kickret_yds , defense_qb_hits ,  defense_sacks , defense_tackles_assists , defense_tackles_combined , defense_tackles_loss , defense_tackles_solo , defense_int , defense_int_td , defense_int_yds , defense_pass_defended , yards_per_play)
```
#Linear Regression Model Summary 

* When looking at the residuals (the difference between actual observed response value and the model's prediction of the response value), there is a mostly symmetrical distribution across these points on the mean value of zero. Therefore, the model predicted points that fall very close to actual observed points. 

* The T-Value is the measure of how many standard deviations the coefficient estimate is from zero. Several predictors are farther away from zero and large relative to standard error such as fourth down conversion attempts (4.875), total yards (5.067), turnovers (-7.378), rushing attempts (5.145), rushing yards (-5.103), defense sacks (7.175), and defense interceptions (5.467) to name a few. 

* The Pr(>|t|) is the probability of observing any value equal or larger than T. A lower P-Value shows that it is unlikely that the relationship between a predictor and the response (total wins) is due to chance. There are 33 predictors with p-values smaller than the 0.05 threshold that can be further analyzed.

* The residual standard error is the measure of the quality of a linear regression fit which can be seen with the plot() function above.

* The adjusted R-squared is used for a Linear Regression model with many variables and is the measure of how well the model fits the actual data. Is it close to 1 and does explain the observed variance in the response variable (number of wins). Therefore, 78.9% of variation in game wins can be explained by our model. 

* And last but not least, the F-statistic. Is there a relationship between predictor and response variables? Since 104 is pretty far from 1, we can reject the null hypothesis and state that there IS indeed a relationship between predictor and repsonse variables. Now to dive into WHICH predictors could predict more wins per season! 

#Possible Predictors

At this point, it's time to play around with some of the predictors. I printed out the predicted wins for each team, each year, based on every predictor. A new data frame is used to store season, predicted wins, and the original data.

I will pick a few predictors with a low T and P value, and that show a significant difference between the league average and the team's statistics from 2020.
```{r}
preds <- predict(lr_model_1, predictors_df) %>% 
        as_tibble() %>% 
        rename(pred_wins = value)

id_df <- team_data_agg %>% 
        ungroup %>% 
        select(season)

pred_df <- bind_cols(predictors_df, preds, id_df) %>% 
       relocate(season, .after = team_name) %>% 
        relocate(pred_wins, .after = season)

apply(team_stats_2020, 2, range)
```
#Philadelphia Eagles Predictions
With a 4 win season in 2020, this model can predict a new number of wins for the Eagles' 2020 season based on a new statistic for one predictor. 

```{r}
league_average_2020 <- team_data_agg %>% 
        filter(season == 2020) %>% 
        group_by(season) %>%
        summarise_if(is.numeric, mean, na.rm =TRUE) %>% 
        mutate(yards_per_play = (passing_yds + rushing_yds) / (passing_att + rushing_att))

team_stats_2020 <-  team_data_agg %>% 
        filter(season == 2020) %>% 
        summarise_if(is.numeric, mean, na.rm =TRUE) %>% 
        mutate(yards_per_play = (passing_yds + rushing_yds) / (passing_att + rushing_att))

eagles_average_2020 <- team_data_agg %>% 
        filter(season == 2020 & team_name == "PHI") %>% 
        mutate(yards_per_play = (passing_yds + rushing_yds) / (passing_att + rushing_att))

#######################

eagles_updated <- pred_df %>%
        filter(season == 2020, team_name=='PHI')

eagles_updated %<>% mutate(total_yards = 4098)


eagles_pred <- predict(lr_model_1, eagles_updated) %>% 
        as_tibble() %>% 
        rename(pred_wins = value)

```
Eagles predicted wins 2020: 3.078381

##First Downs XXX
The Eagles' 2020 number of First Downs was 336. If they increase this to the league average of 347, their predicted wins would be 3.1. With an increase to 400 first downs, their wins would be 3.2

##Time of Possession XXX
The Eagles' 2020 is 28094. If they increase to league average of 28930.56, they could have 3 wins.

Eagles:
60 minutes per game and 17 games
total seconds in all 17 games: 28094
1652 seconds on average in each game = ~ 27.53333 minutes

total minutes possible in 1 game: 60
total minutes possible in 17 games: 17 * 60 = 1020

League:
28930.56 seconds in 17 games
1701 seconds in 1 game = ~ 28 minutes

Max:
33729 in 17 games
1984 seconds in 1 game = 33 minutes

Above Average:
0600 in 17 games = 30 minutes per game

##Fourth Down Conversion Attempts XXX
The Eagles had 35 fourth down conversion attempts in 2020. The league average is 20. If they attempted 12 conversions, their predicted wins goes up to 5. 

##Fourth Down Conversion Completed XX
Eagles:15
Avg:11.3125
Max:19

##Penalties_yds XX
Eagles:853
Avg:779.25
Max:1071
Min:534

##Total Yards ---------------------------
The Eagles' 2020 total yards was 5357.  The league average was 5746.5 and the maximum yards for 2020 was 6652. If the Eagles increase total yards to 6525 yards, they could have won 5 games. League avg from 1970-2020 was 5042 and max amount is 7474. 
Max: 6653
Min: 4478

Increase total yards by 291 to get 5,648 --> 6.654905

##Turnovers XXX
The Eagles had 29 turnovers in 2020 and the league average was 20. With 0 turnovers they will only get to 4.5 wins.

##all_td XX
Eagles:42
Avg:45.5
Max:66

##Fumbles XXX
The Eagles' 2020 was 29, the league's was 20.8. Even with a decrease to 1 fumble, they will not increase to more than 4 wins.

##fumbles_rec - Had the max for this!
Eagles:27
Avg:16.1875
Max:27

##fumbles_rec_yds XX
Eagles:32
Avg:26.3125
Max:147

##Kicking Field Goal Made XXX
The Eagles' 2020 field goals made were 14 (out of 19 attempted) with the leagues being 24.9. If they increase to 30 field goals made, they will still only win 4 games.

## (extra point made)  ---------------------------
Eagles:24
Avg:38.125
Max:59

Attempted 26 extra points, made 24
Out of the 42 touchdowns, they made 24 extra points. That leaves 18 points that could have been scored. Made 7 2-pt conversions for a total of 14 points (missing out on 4 points in the season)

If they made 57, they would have 5.058012 wins. 

##passing_two_pt_md XX Made almost the max!
Eagles:7
Avg:1.9375
Max:8

##passing_rating?? XX
Eagles:1662.8
Avg:1777.784
Max:2194.3

##passing_sacked_yds - Made highest!
Eagles:401
Avg:232
Max:401

##Passing Yards XXX
Eagles 2020: 3728
League 2020: 4003

##punting_tot XX
Eagles:73
Avg: 23.875
Max:82

##punting_blocked XX
Eagles:1
Avg:0.375
Max:3

#punting_yds XX
Eagles:230
Avg:2675.5
Max:3598

##Punt return Total XXX
Eagles scored 23.875 in 2020 and league is 26. Increasing punt return total even to 60 keeps the totals at 4.

##puntret_td XX
Eagles:1
Avg:0.25
Max:1

##puntret_yds XX
Eagles:230
Avg:211.2188
Max:399

##Receiving Yards  ---------------------------
Eagles 2020: 3709
League 2020: 4045.75
Max of 2020: 5005
Max all 5572

4000 gets them 6.175797 wins! ***
5005 gets them 16.87306 wins!

#number of yards gained by a receiver on a passing play – this not only includes the length of the pass, but also the additional yards that the player was able to run once he was in possession of the ball.

##Rushing Attempts   ---------------------------
Eagles: 423.8438
league: 403
Max: 533

423/17 = ~24 per game. 476/17 = ~28

476: 5 wins
533: 6.504194 wins

##Rushing Toudchdowns XXX
Eagles 2020: 16
Max 2020: 30

##Rushing Yards (total number of yards gained by a single player as the result of a rushing play (or plays)) XXX
Eagles 2020 was 1865.438 and league was 2030. If they decrease it to 1600, they would get 5 wins. A decrease to 1750 would be 5 wins, 1230 would be 7 wins.

##kickret_tot XXX
Eagles:31
Avg:30.8125
Max:47

##Defense QB Hits XXX
Eagles had 111 defensive QB hits. The league had 87.6 hits. A decrease to 90 would be 4 wins, to 30 would be 4.5 wins.

##Defense Sacks XXX
Eagles had 48.5 defensive sacks and the league had 35. If they increase to 100 they would increase wins to 5.

##Defense tackles combined XXX
Eagles: 1061
League: 999

##Defense Interceptions XXX
Eagles: 8               League: 12

##Defense interceptions to TD XXX
Eagles: 1
League: 0.96875

##Defense pass defended XXX
Eagles: 42
League: 65.21875

##Yards Per Play  ---------------------------
The Eagles' 2020 Yards Per Play (YPP) was 5.75 and the NFL league's was 6. If the Eagles increased YPP to 6, they could have won ~3.6 games in 2020. If they increased YPP to 7, they could have won ~5.8 games. An increase to 8 could have led to 8 wins. 

6.7 yards per play --> 5 wins

```{r}

jacksonville_average_2020 <- team_data_agg %>% 
        filter(season == 2020 & team_name == "JAX") %>% 
        mutate(yards_per_play = (passing_yds + rushing_yds) / (passing_att + rushing_att))

jacksonville_updated <- pred_df %>%
        filter(season == 2020, team_name=='JAX')

#jacksonville_updated %<>% mutate(passing_two_pt_md = 8)

jacksonville_pred <- predict(lr_model_1, jacksonville_updated) %>% 
        as_tibble() %>% 
        rename(pred_wins = value)
```
With current stats in 2020, they are predicted to score 2.311924 wins.

##Time of Possession: XXX
Jacksonville:26742 --> 2.311924 wins
League: 28930.56 --> 2.254703 wins
Max: 31273 --> 2.193458 wins

##First Downs: XXX
Jacksonville:310 --> 2.311924 wins
League: 347.0625 --> 2.4 wins
Max:397 --> 2.5 wins

##fourth_down_conv_att ??????????
Jacksonville:26 --> 3.17 wins
League: 20.5625 --> 3.64 wins
Max:35 --> 3.38 wins

##fourth_down_conv_cmp XXX
Jacksonville: 7 
League: 11.3125 --> 2.5
Max:19 --> 2.85 wins

##penalties_yds   They had the max of penalties! ----------------------
Jacksonville:1071
League:779.25 --> 2.79 wins
Max:1071
Min:534 --> 3.19 wins

##total_yards  ----------------------
Jacksonville:5227
League: 5746.5 --> 3.17 wins
Max:6653 --> 4.66 wins

##turnovers XXX
Jacksonville:25
League: 20.78125 --> 2.53 wins
Max: 32

18 --> 2.68 wins
16 --> 2.78 wins

##all_td ??????????????
Jacksonville: 36
League:45.5 --> 3.1
Max:66 --> 4.8 wins

##fumbles XXX
Jacksonville:15
League: 18.3125 
Max: 31

##fumbles_rec XXX
Jacksonville: 8 
League:16.1875
Max:27

If recovered all 15 fumbles --> 2.6 wins

##fumbles_rec_yds XXX
Jacksonville: 23
League:26.3125 --> 2.3 wins
Max: 147

##kicking_fgm ----------------------
Jacksonville: 18 - 
League: 24.875/25 --> 2.76 wins
29 --> 3 wins
Max: 38 --> 3.6

attempt: 25, and only made 18

##kicking_xpm (attemp = 28) 
Jacksonville: 24
League:38.125
Max:59

36 total touchdowns. Attempted to kick 28 extra points but made 24. Made 3 2-point conversions

##passing_two_pt_md XXX
Jacksonville: 3
League:1.9375
Max:8

##passing_rating XXX
Jacksonville: 1438.1
League:1777.784
Max:2194.3

##passing_sacked_yds ???????
Jacksonville: 243
League:232
Max:401

##passing_yds XXX
Jacksonville:3955
League: 4003.156
Max:4843

##puntret_tot
Jacksonville:18
League: 23.875 --> 2.47
Max:39 --> 2.88

##punting_blocked XXX
Jacksonville: 0
League:0.375
Max:3

##punting_yds XXX
Jacksonville: 3051
League:2675.5
Max:3598

##puntret_td XXX
Jacksonville: 1
League:0.25
Max:1

##puntret_yds
Jacksonville: 205
League:211.2188 
Max:399 --> 2.56

##receiving_yds  WOW!
Jacksonville:3927
League: 4045.75 --> 3.58
Max: 5005 --> 13.79

##rushing_att    WOW!
Jacksonville:321
League: 423.8438 --> 5 wins
Max: 533 --> 7.9 wins

##rushing_td XXX
Jacksonville:9
League: 16.375
Max: 30

##rushing_yds XXX
Jacksonville:1457
League: 1865.438
Max: 2926

##kickret_tot XXX
Jacksonville: 30
League:30.8125
Max:47

##defense_qb_hits XXX
Jacksonville: 69
League: 87.59375
Max: 134

##defense_sacks
Jacksonville: 17
League: 35.09375 --> 3 wins
Max: 56.0 --> 3.86

##defense_tackles_combined XXX
Jacksonville: 1016
League:999
Max:1079

##defense_int
Jacksonville:12
League: 12.1875
Max: 18 --> 2.7 wins

##defense_int_td XXX
Jacksonville:1
League: 0.96875
Max: 4

##defense_pass_defended
Jacksonville:60
League: 65.21875
Max:86 --> 2.6 wins

##yards_per_play    ------------------------------
Jacksonville:5.77588
League: 6.009248 --> 2.8 wins
Max:7.088764 --> 5.2 wins

```{r}
jets_average_2020 <- team_data_agg %>% 
        filter(season == 2020 & team_name == "NYJ") %>% 
        mutate(yards_per_play = (passing_yds + rushing_yds) / (passing_att + rushing_att))

jets_updated <- pred_df %>%
        filter(season == 2020, team_name=='NYJ')

#jets_updated %<>% mutate(first_downs = 347.0625)

jets_pred <- predict(lr_model_1, jets_updated) %>% 
        as_tibble() %>% 
        rename(pred_wins = value)

```
Jets predicted wins 2020 = 3.559267

##Time of Possession: XXX
jets: 26784-->  wins
League: 28930.56 --> 3.5 wins
Max: 31273 --> 3.4 wins

##First Downs: XXX
jets: 269 -->  wins
League: 347.0625 --> 3.7 wins
Max:397 --> 3.87 wins

##fourth_down_conv_att XXX
jets: 18
League: 20.5625 --> 3.34 wins
Max:35 --> 2

##fourth_down_conv_cmp ---------------------
jets: 7
League: 11.3125 --> 3.75
Max:19 --> 4.1 wins

##penalties_yds  ---------------------
jets:952
League:779.25 --> 3.84
Max:1071
Min:534 --> 4.2 wins

##total_yards  ---------------------
jets:4478
League: 5746.5 --> 5.6 wins
6000 --> 6 wins
Max:6653 --> 7.1 wins

##turnovers 
jets:19
League: 20.78125 
16 --> 3.7
10 turnovers --> 4 wins
Max: 32

##all_td  ---------------------
jets:25
31 --> 4 wins
League:45.5 --> 5.3
55 -->6 wins
Max:66

##fumbles XXX
jets: 8
League: 18.3125 -->  wins
Max: 31

##fumbles_rec
jets: 11
League:16.1875 --> 3.78 wins
22 recovered --> 4 wins
Max:27

##fumbles_rec_yds XXX
jets:11
League:26.3125 --> 3.49
Max:147

##kicking_fgm ??  
#Attempted 28 field goals, made 21
jets:21
League: 24.875 -->  wins
28 --> 3.48 wins
Max: 38 --> 3.44 wins

##kicking_xpm 
#total touchdowns = 25. 
#attempted 24 extra points.
#Made 20.
jets:20
25 --> 2.85 wins
30 --> 4.1 wins (moot point?)
League: 38.125 --> 4.6
Max:59

##passing_two_pt_md XXX
jets:1
Max:8

##passing_rating XXX
jets:1336.2
League:1777.784
Max:2194.3

##passing_sacked_yds XXX
jets:298
League:232
Max:401

##passing_yds XXX
jets:2853
League: 4003.156
Max:4843

##puntret_tot ??
jets:10
League: 23.875 --> 3.9 wins
Max:39 --> 4.3

##punting_blocked XXX
jets:0
League:0.375
Max:3

##punting_yds highest yards
jets:3598
League:2675.5
Max:3598

##punting_tot X
jets:82
League:58.28125
105 --> 4 wins

##puntret_td XXX
jets:0
League:0.25
Max:1

##puntret_yds 
jets:86
League:211.2188 --> 3.7 wins
Max:399
440 --> 4 wins

##receiving_yds WOW!   ---------------------
jets:3066
3210 --> 5 wins
League: 4045.75 --> 13.98 wins
Max: 5005 --> 24 wins

##rushing_att   ---------------------
jets:404
League: 423.8438 --> 4 wins
460 --> 5 wins
Max: 533 --> 6.95 wins

##rushing_td XXX
jets:8
League: 16.375
Max: 30

##rushing_yds XXX
jets:1674
League: 1865.438
Max: 2926

##kickret_tot XXX
jets:40
League:30.8125
Max:47

##defense_qb_hits XXX
jets:85
League: 87.59375
Max: 134

##defense_sacks 
jets:31
League: 35.09375 --> 3.7
Max: 56.0 --> 3.7

##defense_tackles_combined  Had the highest!
jets:1079
League:999
Max:1079

##defense_int 
jets:10
League: 12.1875 --> 3.6 wins
Max: 18 --> 4 wins

##defense_int_td XXX
jets:1
League: 0.96875
Max: 4

##defense_pass_defended XXX
jets:67
League: 65.21875
Max:86 --> 3.79

##yards_per_play WOW __________________
jets: 5.156036
League: 6.009248 --> 5.43
Max:7.088764 --> 7.8 wins!
